Aspects of RDF Data Constraints in the Social, Behavioural and Economic Sciences

### 2015-04-30 paper/paper7/paper7.tex
struktur
evaluation

\ke{da muss mindestens ein überleitender satz rein, der noch mal den unterschied von constraint types und types aufgreift und erklärt, dass es jetzt um konkrete constraints auf den vokabularen geht, deren severity eben vom konkreten kontext abhängt und nicht allgemein über den type bestimmt werden kann.}

\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.\ke{oder etwas weniger anmaßend: we use the commonly accepted classification of log messages in software development and distingush informational, warning and error.}
According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt... mein vorschlag von eben kann das komplett ersetzen.}
\begin{itemize}
	\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
\end{itemize}
Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
their default severity levels are in most cases very strong (\emph{error}) and 
in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
\ke{den ganzen letzten absatz finde ich unübersichtlich. Kann man das nicht klarer sagen: Error sind syntaktische oder semantische fehler, die zu einem abbruch der datenverarbeitung führen sollten. warnings sind syntaktische oder semantische fehler, die aber normalerweise nicht zu einem abbruch führen müssen. verletzungen von informational constraints weisen auf potentielle verbesserungen in den daten hin, werden aber nicht als fehler angesehen (der satz war in ordnung). die fussnote ist doch vollkommen fehl am platz, oder? es werden ja nicht alle constraints aufgelistet und wie ihr das implementiert habt und ob ihr euch arbeit erspart habt weil ihr default severity bei bestimmten constraint types vorgebt, das interessiert doch keinen.}

>>>>

A concrete constraint is instantiated from one of the 82 constraint types and is defined for a specific vocabulary.
It does not make sense to determine the severity of constraint violations of a constraint type,
as the severity of the violation of a given constraint depends on the individual context and vocabulary.
%as the violation of one constraint may be severe,
%whereas, the violation of another constraint of the same type may be minor.
\emph{SBE} experts determined the default \textbf{\emph{severity level}} (\emph{R-158}) for each of the 246 constraints to indicate how serious the violation of the constraint is.
We propose an extensible metric to measure the continuum of severity levels ranging from \emph{informational} to \emph{error}.\ke{oder etwas weniger anmaßend: we use the commonly accepted classification of log messages in software development and distingush informational, warning and error.}
According to the default severity level of constraints, the complete set of constraints encompasses three disjoint \emph{sets of constraints}:\ke{auch dieser satz macht keinen sinn für mich, ebensowenig wie die extrem erhellende auflistung, die gleich folgt... mein vorschlag von eben kann das komplett ersetzen.}
\begin{itemize}
	\item \textbf{\emph{informational constraints}}: constraints with severity level \emph{informational}
	\item \textbf{\emph{warning constraints}}: constraints with severity level \emph{warning}
	\item \textbf{\emph{error constraints}}: constraints with severity level \emph{error}
\end{itemize}
Violations of \emph{informational constraints} point to desirable but not necessary data improvements to achieve RDF representations which are ideal in terms of syntax and semantics of used vocabularies. 
Data not conforming to \emph{warning} and \emph{error constraints} is syntactically and/or semantically not correctly represented.
Data not conforming to \emph{warning constraints} but to \emph{error constraints} could be processed further.
Data not corresponding to \emph{error constraints}, however, cannot be processed further after validation. 
As the purpose of \emph{vocabulary constraints} is to ensure explicitly stated semantics of vocabularies, 
their default severity levels are in most cases very strong (\emph{error}) and 
in average stronger than the severity levels of \emph{simple} and \emph{complex constraints}.
As a consequence, violating many \emph{vocabulary constraints} is an indicator for bad (meta)data quality\footnote{For simplicity reasons, we only assign severity levels to \emph{vocabulary constraints} in this paper in case they differ from \emph{error constraints}.}.
\ke{den ganzen letzten absatz finde ich unübersichtlich. Kann man das nicht klarer sagen: Error sind syntaktische oder semantische fehler, die zu einem abbruch der datenverarbeitung führen sollten. warnings sind syntaktische oder semantische fehler, die aber normalerweise nicht zu einem abbruch führen müssen. verletzungen von informational constraints weisen auf potentielle verbesserungen in den daten hin, werden aber nicht als fehler angesehen (der satz war in ordnung). die fussnote ist doch vollkommen fehl am platz, oder? es werden ja nicht alle constraints aufgelistet und wie ihr das implementiert habt und ob ihr euch arbeit erspart habt weil ihr default severity bei bestimmten constraint types vorgebt, das interessiert doch keinen.}
